### 2014-10-30 motivation.tex
edits
Edits

\begin{figure}
\begin{codehaskell}
data Effect, Rel, Prop, Fol
type Contract = Effect -> Fol

@@

There are no restrictions on when and how a \cf{deposit} operation can execute.
Hence, the deposit contract imposes no consistency restrictions.

@@

>>>>

\begin{figure}
%Careful while adjsting spaces in the following code; screws "::" alignment.
\begin{codehaskell}
data Effect, Rel, Prop, Fol
type Contract = Effect -> Fol

@@

There are no restrictions on when and how a \cf{deposit} operation can execute.
Hence, the deposit contract imposes no consistency restrictions. The deposit
contract is:

@@

\subsection{Putting it together}

The combines the RDT implementation along with the contracts to instantiate a
new RDT as follows:

\begin{codehaskell}
mkRDT [(Deposit, deposit, $(chk depositCtrt)),
  (Withdraw, withdraw, $(chk withdrawCtrt)),
	(GetBalance, getBalance, $(chk getBalanceCtrt))]
\end{codehaskell}

\noindent The function \cf{chk} analyzes the contract and maps it to one of the
available store consistency levels. From the perspective of the client of \name
store, the store is organized as a collection of key-indexed, object-valued
tables, where each object in a table has the same type. Clients invoke
operations using the following primitive:

\begin{codehaskell}
data Quelea a
instance Monad Quelea
invoke :: (Arg a, Res r)
			 => Key -> OperName -> a -> Quelea r
\end{codehaskell}
